Self Regulation Ontology Retest Data Report

### 2017-04-23 SRO_Report.Rmd
got bootstrapping function working

bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
  tmp_sample = sample_workers()
  get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, format='wide')
  get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, format='wide')
  get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample, format='wide')
}

sample_workers()

>>>>

bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
  tmp_sample = sample_workers()
  out_df = data.frame(dv = dv_var)
  out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  return(out_df)
}

bootstrap_relialibility(dv_var = numeric_cols[1])
